paper_replication

### 2021-12-14 paper_replication.Rmd
Update paper_replication.Rmd

TODO: classify counties as highly restrictive or not
    - option 1: we can use the summary data that Alice linked to
    (https://www.guttmacher.org/article/2019/08/state-abortion-policy-landscape-hostile-supportive)
    - option 2: dig through the detailed legislation data and use the 3/4 types classification they did in the paper (http://lawatlas.org/datasets/abortion-laws)
    I'd say let's start with the summary data, and we do the extra work to make a more faithful replication later if we have time at the end.

@@

abortions2010$county <- gsub(abortions2010$county, pattern = "[()]", replacement = "")

abortions2010$county <- gsub(abortions2010$county, pattern = "ind. city", replacement = "city")

abortions2010$county <- gsub(abortions2010$county, pattern = "Saint", replacement = "St.")

abortions2010$county <- gsub(abortions2010$county, pattern = "Dekalb", replacement = "DeKalb")

abortions2010$county <- gsub(abortions2010$county, pattern = "Desoto", replacement = "DeSoto")

abortions2010$county <- gsub(abortions2010$county, pattern = "Miami Dade", replacement = "Miami-Dade")

abortions2010$county <- gsub(abortions2010$county, pattern = "Hawai'i", replacement = "Hawaii")

abortions2010$county <- gsub(abortions2010$county, pattern = "Kaua'i", replacement = "Kauai")

abortions2010$county <- gsub(abortions2010$county, pattern = "City", replacement = "city")

countydem$county <- gsub(countydem$county, pattern = "City", replacement = "city")

abortions2010$county <- gsub(abortions2010$county, pattern = "Lac Qui Parle", replacement = "Lac qui Parle")

abortions2010$county <- gsub(abortions2010$county, pattern = "St.e Genevieve", replacement = "Ste. Genevieve")

abortions2010$county <- gsub(abortions2010$county, pattern = "Shannon/Oglala Lakota", replacement = "Oglala Lakota")

abortions2010$county <- gsub(abortions2010$county, pattern = "Lamoure", replacement = "LaMoure")

>>>>

@@

abortions2010$county <- gsub(abortions2010$county, pattern = "[()]", replacement = "")
abortions2010$county <- gsub(abortions2010$county, pattern = "ind. city", replacement = "city")
abortions2010$county <- gsub(abortions2010$county, pattern = "Saint", replacement = "St.")
abortions2010$county <- gsub(abortions2010$county, pattern = "Dekalb", replacement = "DeKalb")
abortions2010$county <- gsub(abortions2010$county, pattern = "Desoto", replacement = "DeSoto")
abortions2010$county <- gsub(abortions2010$county, pattern = "Miami Dade", replacement = "Miami-Dade")
abortions2010$county <- gsub(abortions2010$county, pattern = "Hawai'i", replacement = "Hawaii")
abortions2010$county <- gsub(abortions2010$county, pattern = "Kaua'i", replacement = "Kauai")
abortions2010$county <- gsub(abortions2010$county, pattern = "City", replacement = "city")
countydem$county <- gsub(countydem$county, pattern = "City", replacement = "city")
abortions2010$county <- gsub(abortions2010$county, pattern = "Lac Qui Parle", replacement = "Lac qui Parle")
abortions2010$county <- gsub(abortions2010$county, pattern = "St.e Genevieve", replacement = "Ste. Genevieve")
abortions2010$county <- gsub(abortions2010$county, pattern = "Shannon/Oglala Lakota", replacement = "Oglala Lakota")
abortions2010$county <- gsub(abortions2010$county, pattern = "Lamoure", replacement = "LaMoure")
